Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-09-22 tex/sup/supplementary_information.tex
编译测试

Multiple datasets were used in this study. 
\subsection*{Statistical datasets}
The 2nd National Water Resources Assessment Program.

>>>>

Multiple types of dataset were used in this study. 
\subsection*{Statistical datasets}
For statistics, we used GDP data, statistical yearbook data, and data extracted from the 2nd National Water Resources Assessment Program
\cite{zhouDecelerationChinaHuman2020}.
